---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
activity <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?
1.Total steps per day
```{r}
StepsPerDay <- aggregate(activity$steps, list(activity$date), FUN=sum)
colnames(StepsPerDay) <- c("Date", "Steps")
StepsPerDay
```
2. Make a histogram of the total number of steps taken each day

```{r}
hist(StepsPerDay[,2],main='Steps per Day' ,col='blue')
```
3.Calculate and report the **mean** and **median** total number of steps taken per day

```{r}
mean(StepsPerDay[,2],na.rm=TRUE)
median(StepsPerDay[,2],na.rm=TRUE)
```
## What is the average daily activity pattern?
```{r}
StepsPerTime <- aggregate(steps~interval,data=activity,FUN=mean,na.action=na.omit)
plot(StepsPerTime,type='l',col='green',main="Average steps per time interval",xlab="Time" ,ylab="Steps")
```

# table for dplyr

library(dplyr)
ST <- tbl_df(StepsPerTime)
# find the column
ST %>% select(time, steps) %>% filter(steps==max(ST$steps))


## Imputing missing values,



## Are there differences in activity patterns between weekdays and weekends?
